---
output: html_document
editor_options: 
  chunk_output_type: console
---
Created: 01/29/21
Last modified: 01/29/21



Jasons comment on CCP MEthods Jan 2021
Do the PCA on hypothetical data combined with a retrospective power analysis
SO FIRST do the power analysis
In mice and humans 




```{r load libraries, eval=TRUE, message=FALSE}
setwd("C:/Users/Zsuzsi/Documents/Lerch/TideData_ForPaper")

library(ggplot2)
library(grid)
library(MRIcrotome)
library(devtools)
library(ggfortify)
library(fitdistrplus)
library(MASS)
library(splines)
library(tidyverse)
library(RMINC)
library("ggpubr")
library("lme4")
library(lenses)
#library("lme4", lib.loc="/axiom2/projects/software/arch/linux-xenial-xerus/RMINC/1.5.1.0") <- previously, but this errored so running above command 
```




#Load in all data

##Mouse Behaviour

```{r Mouse Behav compiled data, echo=TRUE,eval=TRUE}
tf <- read.csv("CompiledBehavData_Tide_WithAllBehav_USE.csv")

tf$Genotype <- relevel(tf$Genotype %>% as.factor(), ref="Wt")
tf$Treatment <- relevel(tf$Treatment%>% as.factor(), ref="Placebo")
tf$StrainW <- relevel(tf$StrainW%>% as.factor(), ref="Wt")

tf0 <- subset(tf, Group != 0)

with(tf, table(StrainW, Treatment))
with(tf0, table(StrainW, Treatment))

names(tf)
```


##Mouse Brain

```{r Mouse Brain  compiled data, echo=TRUE,eval=TRUE}
#Now (June 19, 2019)
#Missing 6 mice from chunk 4 that had failed MAGeTs
ADE <- read.csv("TideExVivo_AllData_nottrans.csv")

ADE$Genotype <- ADE$Genotype %>% as.factor %>% relevel(., ref="Wt")
ADE$StrainW <- ADE$StrainW %>% as.factor %>%relevel(., ref="Wt")
ADE$Treatment <- ADE$Treatment %>% as.factor %>%relevel(., ref="Placebo")

```


#Combine mice brain & behav
```{r Mouse Brain  compiled data, echo=TRUE,eval=TRUE}
#Combine brain and behav
mice <- left_join(tf, ADE, by=c("Group", "ID", "Strain", "StrainW", "Genotype", "Treatment", "GenotypeW","Cage"))



#Complete cases brain

micec <- mice[complete.cases(mice$Labels),] 

#Complete cases behav
micecc <- micec %>%
    select(Group:YMBlockedPref,amygdala:brainvolumes) %>%
    filter(is.na(FCHabituation)==FALSE,
           !is.na(FCPostUS),        
           !is.na(FCContext),                                              
           !is.na(FCAltContext),                                            
           !is.na(FCCued),
           !is.na(OMRatioDur),
           !is.na(OMRatioFreq),  
           !is.na(OMDistance),
           !is.na(OMMoving),
           !is.na(OMRawOpenDur),
           !is.na(OMRawOpenFreq),
           !is.na(OFCenter),
           !is.na(OFDist),
           !is.na(YMRawStart),  
           !is.na(YMRawOther),               
           !is.na(YMBlockedPref)) 
           
                                                     



#Better to have all variables scaled to positive end (higher numbers means good (i.e. higher latency means better memory)) so make them negative if they are not in the right direction (GrAvgDur, GrNumBouts, and RotPreTrials need to be flipped!)(the rest are good... though OFDist is debateable)


miceccp <- micecc %>% 
  mutate(FCHabituation2= -FCHabituation,
         FCPostUS2= -FCPostUS,
         FCAltContext2= -FCAltContext,
         YMRawStart2= -YMRawStart,
         YMRawOther2= - YMRawOther) %>%
  select(-c(FCHabituation,FCPostUS,FCAltContext,YMRawStart,YMRawOther))

```







#POWER TEST MICE

lets start with amygdala, striatum, thalamus (three regions that are fairly easily across the two species)

humans are all split volumes, so just taking right to amke things easier for now:
right.amygdala (369), right.stiatum(370), right.thalamus(372)


lets use anxiet and memory, since those overlap the humans the most 
#Mem, Mem2, Mem3
  #NEPSY is split by age and only done 3-16yrs
  #We have Nenps 3-4 (Mem3), nepsy 5-16(Mem2), and other (Mem)
#Anx, Anx2
  #SPENCE for young, RCADS for older

We don't hav ememory so let's do hyperactivity instead: OMMoving and ABC hyperactivity subscale (4)

```{r human behav- load}

HBI_USE <- read.csv("Human_TIDEdata_TideBehav_USE.csv")

HBI_VARS <- HBI_USE %>% select(Subject, RAND_TREATMENT, AGE_AT_ENROLLMENT, GENDER, Variant, Type,CSHQ_BEDTIME_RESIS:CSHQ_TOTAL, RCAD_SA_TSCORE:RCAD_ANXDEPTOTAL, ends_with("_TOTAL"), MD_CONTENT_SCORE:MD_CONTRAST_S_SCR,MDD_CONTENT_SCR:MD_MDD_CNTRST_S_SCR,ABC_SUBSCALE_I:ABC_SUBSCALE_V, ends_with("_STD"))%>% select(-CSHQ_SLPY_DRSNG_STD, -CSHQ_SLPY_PLY_OTH_STD,-CSHQ_SLPY_BTHRM_STD)



with(HBI_VARS, table(RAND_TREATMENT))

```



```{r Human brain- load}

HIm <- read.csv("Human_TIDEimaging_USE.csv")

HI <- HIm %>% group_by(subject) %>% arrange(subject)

HIU <- HI %>% mutate(Subject= gsub("-","", subject %>% gsub("MR160","",.)))

HIU$Subject <- HIU$Subject %>% as.numeric()

HI_USE <- HIU %>% filter(MAGeT_QC=="TRUE")


# combine treat and image

BBB2 <- HBI_USE %>% rename(Site=Site.x) %>% select(Subject:Inheritance, Site:RAND_TREATMENT) 

Img <- inner_join(BBB2, HI_USE, by="Subject")

nrow(Img)
unique(Img$Subject)

```


```{r combine human brain and behav}

HIL <- Img %>% filter(Point=="post") %>% filter(Sex=="M") %>% filter(QC_LITE==TRUE)


Comb <- HIL %>% left_join(HBI_VARS, by="Subject")


```

right.amygdala (380), right.stiatum(381), right.thalamus(383)

lets use anxiet and memory, since those overlap the humans the most 
#Mem, Mem2, Mem3
  #NEPSY is split by age and only done 3-16yrs
  #We have Nenps 3-4 (Mem3), nepsy 5-16(Mem2), and other (Mem)
#Anx, Anx2
  #SPENCE for young, RCADS for older


  
  RCAD_ANXIETYTOTAL (436)
  MDD_TOTAL_SCORE (457)
  
  FCContext
  OFCenter

```{r power analysis mice}


micew <- miceccp %>% filter(Genotype=="Wt", Treatment=="Placebo")

#OFDist, FCContext, amygdala, striatum, thalamus
get_summary_stats(micew[,c(19,11, 23,70, 73)])

dat <- get_summary_stats(micew[,c(19,11, 23,70, 73)]) %>% select(variable,mean,sd)



dat$pd5 <- 0
dat$pd10 <- 0
dat$pd15 <- 0
dat$pd20<- 0
dat$pd25 <- 0
dat$pd40 <- 0
dat$pd50 <- 0
dat$pd100 <- 0

for (i in 1:nrow(dat)){
  
  mn <- dat$mean[i]
  ssd <- dat$sd[i]
  
  dt <- power.t.test(n=5, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd5[i] <- dt/mn*100
  
    dt <- power.t.test(n=10, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd10[i] <- dt/mn*100
  
    dt <- power.t.test(n=15, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd15[i] <- dt/mn*100
  
    dt <- power.t.test(n=20, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd20[i] <- dt/mn*100
  
    dt <- power.t.test(n=25, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd25[i] <- dt/mn*100
  
      dt <- power.t.test(n=40, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd40[i] <- dt/mn*100 
   
    dt <- power.t.test(n=50, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd50[i] <- dt/mn*100 
  
      dt <- power.t.test(n=100, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd100[i] <- dt/mn*100 
  
}


datl <- dat %>% pivot_longer(cols=pd5:pd100, names_to="samples",values_to="perc.diff")
datl <- datl %>% mutate(smp= case_when(samples=="pd5"~5, 
                        samples=="pd10"~10,
                        samples=="pd15"~15,
                        samples=="pd20"~20,
                        samples=="pd25"~25,
                        samples=="pd40"~40,
                        samples=="pd50"~50,
                        samples=="pd100"~100))



f <- ggplot(datl, aes(y=perc.diff, x=smp, fill=variable, color=variable))
f <- f + theme_bw(28)
f <- f + geom_point(data=datl %>% filter(smp !=100 & perc.diff<75), aes(y=perc.diff, group=variable, fill=variable, x=smp), position = position_jitterdodge(), shape=21, size=4)  
f <- f + xlab("Sample size") + ylab("Percent Difference")
f <- f + scale_fill_hue(name="Variable", breaks=c("FCContext", "OFCenter", "amygdala", "striatum", "thalamus"), labels=c("Memory", "Anxiety", "Amygdala", "Striatum", "Thalamus"))
#f <- f + geom_smooth(aes(group=variable), method="glm")
f <- f + ggtitle("Power Analysis: Mice") +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
f <- f + theme(legend.title= element_text(size=28))
f <- f + theme(legend.text= element_text(size=20))
f

ggsave("Tide_PowerMice.png",f, width=12, height=8)



```


#Now repeat but for humans

lets start with amygdala, striatum, thalamus (three regions that are fairly easily across the two species)

humans are all split volumes, so just taking right to amke things easier for now:
right.amygdala (380), right.stiatum(381), right.thalamus(383)


lets use anxiet and memory, since those overlap the humans the most 
  #Mem, Mem2, Mem3
  #NEPSY is split by age and only done 3-16yrs
  #We have Nenps 3-4 (Mem3), nepsy 5-16(Mem2), and other (Mem)
  
  
  RCAD_ANXIETYTOTAL (436)
  MDD_TOTAL_SCORE (457)
  

```{r power analysis humans, eval=TRUE, message=FALSE}
combw <- Comb %>% filter(RAND_TREATMENT.x=="PLACEBO")

#  RCAD_ANXIETYTOTAL, ABC_SUBSCALE_IV, amygdala, striatum, thalamus
get_summary_stats(combw[,c(380, 381, 383, 436, 457)])

dat <- get_summary_stats(combw[,c(380, 381, 383, 436, 457)]) %>% select(variable,mean,sd)



dat$pd5 <- 0
dat$pd10 <- 0
dat$pd15 <- 0
dat$pd20<- 0
dat$pd25 <- 0
dat$pd40 <- 0
dat$pd50 <- 0
dat$pd100 <- 0

for (i in 1:nrow(dat)){
  
  mn <- dat$mean[i]
  ssd <- dat$sd[i]
  
  dt <- power.t.test(n=5, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd5[i] <- dt/mn*100
  
    dt <- power.t.test(n=10, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd10[i] <- dt/mn*100
  
    dt <- power.t.test(n=15, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd15[i] <- dt/mn*100
  
    dt <- power.t.test(n=20, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd20[i] <- dt/mn*100
  
    dt <- power.t.test(n=25, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd25[i] <- dt/mn*100
  
      dt <- power.t.test(n=40, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd40[i] <- dt/mn*100 
   
    dt <- power.t.test(n=50, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd50[i] <- dt/mn*100 
  
      dt <- power.t.test(n=100, sd=ssd, sig.level=0.05, power=.8)$delta
  dat$pd100[i] <- dt/mn*100 
  
}


datl <- dat %>% pivot_longer(cols=pd5:pd100, names_to="samples",values_to="perc.diff")
datl <- datl %>% mutate(smp= case_when(samples=="pd5"~5, 
                        samples=="pd10"~10,
                        samples=="pd15"~15,
                        samples=="pd20"~20,
                        samples=="pd25"~25,
                        samples=="pd40"~40,
                        samples=="pd50"~50,
                        samples=="pd100"~100))



f <- ggplot(datl, aes(y=perc.diff, x=smp, fill=variable, color=variable))
f <- f + theme_bw(28)
f <- f + geom_point(data=datl %>% filter(smp !=100 & perc.diff<75), aes(y=perc.diff, group=variable, fill=variable, x=smp), position = position_jitterdodge(), shape=21, size=4)
f <- f + xlab("Sample size") + ylab("Percent Difference")
f <- f + scale_fill_hue(name="Variable", breaks=c("MDD_TOTAL_SCORE", "RCAD_ANXIETYTOTAL", "right.amygdala", "right.striatum", "right.thalamus"), labels=c("Memory", "Anxiety", "Amygdala", "Striatum", "Thalamus"))
#f <- f + geom_smooth(aes(group=variable), method="glm")
f <- f + ggtitle("Power Analysis: Humans") +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
f <- f + theme(legend.title= element_text(size=28))
f <- f + theme(legend.text= element_text(size=20))
f

ggsave("Tide_PowerHumans.png",f, width=12, height=8)



```

##Continued power analysis on mice, comparing to literature and expanding to other behaviours

```{r power analysis mice expanded, eval=TRUE, message=FALSE}
Previous <- read.csv("FMR1BehavValidationSheet.csv") %>% filter(Study != "CCP")

PA <- Previous %>% filter(Genotype=="Wt") %>% rename(mean=Mean, sd=SD, variable=Variable) %>% select(Behaviour:Study, variable, mean, sd) %>%  filter(complete.cases(sd))


micew <- miceccp %>% filter(Genotype=="Wt", Treatment=="Placebo")

#OFDist, FCContext, amygdala, striatum, thalamus, OMDistance, OFDist
get_summary_stats(micew[,c(19,11, 23,70, 73,15,20)])

dat <- get_summary_stats(micew[,c(19,11, 23,70, 73,15,20)]) %>% select(variable,mean,sd)

dat$Behaviour <- c("Brain", "Memory", "Anxiety", "Brain", "Brain", "Hyperactivity", "Hyperactivity")
dat$Test <- c("Amygdala", "FC", "Open Field", "Striatum", "Thalamus", "Omaze", "Open Field")
dat$Study <- rep("Tideglusib", nrow(dat))

PB <- rbind(PA, dat)

PB <- PB %>% unite(Name, Behaviour, Study, sep="_", remove=FALSE) 


PB$pd5 <- 0
PB$pd10 <- 0
PB$pd15 <- 0
PB$pd20<- 0
PB$pd25 <- 0
PB$pd40 <- 0
PB$pd50 <- 0
PB$pd100 <- 0

for (i in 1:nrow(PB)){
  
  mn <- PB$mean[i]
  ssd <- PB$sd[i]
  
  dt <- power.t.test(n=5, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd5[i] <- dt/mn*100
  
    dt <- power.t.test(n=10, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd10[i] <- dt/mn*100
  
    dt <- power.t.test(n=15, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd15[i] <- dt/mn*100
  
    dt <- power.t.test(n=20, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd20[i] <- dt/mn*100
  
    dt <- power.t.test(n=25, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd25[i] <- dt/mn*100
  
      dt <- power.t.test(n=40, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd40[i] <- dt/mn*100 
   
    dt <- power.t.test(n=50, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd50[i] <- dt/mn*100 
  
      dt <- power.t.test(n=100, sd=ssd, sig.level=0.05, power=.8)$delta
  PB$pd100[i] <- dt/mn*100 
  
}


PBl <- PB %>% pivot_longer(cols=pd5:pd100, names_to="samples",values_to="perc.diff")
PBl <- PBl %>% mutate(smp= case_when(samples=="pd5"~5, 
                        samples=="pd10"~10,
                        samples=="pd15"~15,
                        samples=="pd20"~20,
                        samples=="pd25"~25,
                        samples=="pd40"~40,
                        samples=="pd50"~50,
                        samples=="pd100"~100))




colurs <- c("#1f78b4","#1f78b4","#fb9a99","#33a02c","#33a02c","#b2df8a","#b2df8a","#33a02c","#33a02c","#1f78b4","#1f78b4","#b2df8a" ,"#cab2d6","#cab2d6","#cab2d6","#fdbf6f","#ff7f00","#ff7f00","#ff7f00","#a6cee3","#a6cee3","#a6cee3","#a6cee3","#e31a1c","#e31a1c","#e31a1c","#e31a1c","#e31a1c","#e31a1c","#e31a1c")
  
  
countryColors <- data.frame(cbind(PB$Name,colurs)) %>% rename(Country=V1)


#colours:

#a6cee3 ellegood 
#1f78b4 impc
#b2df8a mineur 
#33a02c nielsen
#fb9a99 peier
#e31a1c tideglusib
#fdbf6f dobkin
#ff7f00 paradee
#cab2d6 vanDam

jColors <- countryColors$colurs
names(jColors) <- countryColors$Country
head(jColors)


#seperating anxiety

PBla <- PBl %>% filter(Behaviour=="Anxiety")


f <- ggplot(PBla, aes(y=perc.diff, x=smp, fill=Name))
f <- f + theme_bw(28)
f <- f + geom_point(data=PBla %>% filter(smp !=100), aes(y=perc.diff, group=Name, fill=Name, x=smp), position = position_jitterdodge(), shape=21, size=4)  
f <- f + xlab("Sample size") + ylab("Percent Difference")
f <- f + ggtitle("Power Analysis: Anxiety in Mice") +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
f <- f + theme(legend.title= element_text(size=28))
f <- f + scale_fill_manual(values=jColors)
f <- f + theme(legend.text= element_text(size=20))
f <- f + coord_cartesian(ylim=c(0,200))
f <- f + facet_grid(~Test)
f
ggsave("Tide_PowerMice_Anxiety.png",f, width=12, height=8)





#seperating memory

PBlm <- PBl %>% filter(Behaviour=="Memory")

f <- ggplot(PBlm, aes(y=perc.diff, x=smp, fill=Name))
f <- f + theme_bw(28)
f <- f + geom_point(data=PBlm %>% filter(smp !=100), aes(y=perc.diff, group=Name, fill=Name, x=smp), position = position_jitterdodge(), shape=21, size=4)  
f <- f + xlab("Sample size") + ylab("Percent Difference")
f <- f + ggtitle("Power Analysis: Memory in Mice") +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
f <- f + theme(legend.title= element_text(size=28))
f <- f + theme(legend.text= element_text(size=20))
f <- f + scale_fill_manual(values=jColors)
f <- f + coord_cartesian(ylim=c(0,200))
f
ggsave("Tide_PowerMice_Memory.png",f, width=12, height=8)




#seperating the rest

PBlo <- PBl %>% filter(Behaviour!="Memory", Behaviour!= "Anxiety")

f <- ggplot(PBlo, aes(y=perc.diff, x=smp, fill=Name))
f <- f + theme_bw(28)
f <- f + geom_point(data=PBlo %>% filter(smp !=100), aes(y=perc.diff, group=Name, fill=Name, x=smp), position = position_jitterdodge(), shape=21, size=4)  
f <- f + xlab("Sample size") + ylab("Percent Difference")
f <- f + ggtitle("Power Analysis: Brain and Hyperactivity in Mice") +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
f <- f + theme(legend.title= element_text(size=28))
f <- f + theme(legend.text= element_text(size=20))
f <- f + scale_fill_manual(values=jColors)
f <- f + coord_cartesian(ylim=c(0,200))
f <- f + facet_grid(~Behaviour)
f
ggsave("Tide_PowerMice_Other.png",f, width=12, height=8)











```






##PCA 






```{r PCA 10% diff anx and amyg, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=100, ncol=7))
dfh <- data.frame(matrix(nrow=100, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfm$Responder <- c(rep("Responder",10), rep("Nonresponder", 90))
dfm$Anxiety <- c(rnorm(10, mean=34.21, sd=20.6),rnorm(90, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(10, mean=10.362, sd=.526),rnorm(90, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfh$Responder <- c(rep("Responder",10), rep("Nonresponder", 90))
dfh$Anxiety <- c(rnorm(10, mean=56.54, sd=17.7),rnorm(90, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(10, mean=1372.8, sd=220),rnorm(90, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Subset treated are weak responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_SubsetResponders_mice_10pdanxamy.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Subset treated are weak responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_SubsetResponders_humans_10pdanxamy.png", c, width=12, height=8)

```




```{r PCA 40% diff anx and amyg, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=100, ncol=7))
dfh <- data.frame(matrix(nrow=100, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfm$Responder <- c(rep("Responder",10), rep("Nonresponder", 90))
dfm$Anxiety <- c(rnorm(10, mean=31.1*1.4, sd=20.6),rnorm(90, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(10, mean=9.42*1.4, sd=.526),rnorm(90, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfh$Responder <- c(rep("Responder",10), rep("Nonresponder", 90))
dfh$Anxiety <- c(rnorm(10, mean=51.4*1.4, sd=17.7),rnorm(90, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(10, mean=1248*1.4, sd=220),rnorm(90, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Subset treated are strong responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_SubsetResponders_mice_40pdanxamy.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Subset treated are strong responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_SubsetResponders_humans_40pdanxamy.png", c, width=12, height=8)

```








```{r PCA 40% diff anx and amyg & most treated respond, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=100, ncol=7))
dfh <- data.frame(matrix(nrow=100, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfm$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfm$Anxiety <- c(rnorm(40, mean=31.1*1.4, sd=20.6),rnorm(60, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(40, mean=9.42*1.4, sd=.526),rnorm(60, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfh$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfh$Anxiety <- c(rnorm(40, mean=51.4*1.4, sd=17.7),rnorm(60, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(40, mean=1248*1.4, sd=220),rnorm(60, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape= "Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are strong responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_mice_40pdanxamy.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are strong responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_humans_40pdanxamy.png", c, width=12, height=8)

```










```{r PCA 20% diff anx and amyg & most treated respond, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=100, ncol=7))
dfh <- data.frame(matrix(nrow=100, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfm$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfm$Anxiety <- c(rnorm(40, mean=31.1*1.2, sd=20.6),rnorm(60, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(40, mean=9.42*1.2, sd=.526),rnorm(60, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfh$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfh$Anxiety <- c(rnorm(40, mean=51.4*1.2, sd=17.7),rnorm(60, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(40, mean=1248*1.2, sd=220),rnorm(60, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are moderate responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_mice_20pdanxamy.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are moderate responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_humans_20pdanxamy.png", c, width=12, height=8)

```



```{r PCA 10% diff anx and amyg & most treated, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=100, ncol=7))
dfh <- data.frame(matrix(nrow=100, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfm$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfm$Anxiety <- c(rnorm(40, mean=34.21, sd=20.6),rnorm(60, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(40, mean=10.362, sd=.526),rnorm(60, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfh$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfh$Anxiety <- c(rnorm(40, mean=56.54, sd=17.7),rnorm(60, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(40, mean=1372.8, sd=220),rnorm(60, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are weak responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_mice_10pdanxamy.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are weak responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_humans_10pdanxamy.png", c, width=12, height=8)

```




```{r PCA 20% diff anx and amyg & subset treated respond, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=100, ncol=7))
dfh <- data.frame(matrix(nrow=100, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfm$Responder <- c(rep("Responder",10), rep("Nonresponder", 90))
dfm$Anxiety <- c(rnorm(10, mean=31.1*1.2, sd=20.6),rnorm(90, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(10, mean=9.42*1.2, sd=.526),rnorm(90, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",50), rep("Placebo", 50))
dfh$Responder <- c(rep("Responder",40), rep("Nonresponder", 60))
dfh$Anxiety <- c(rnorm(10, mean=51.4*1.2, sd=17.7),rnorm(90, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(10, mean=1248*1.2, sd=220),rnorm(90, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Subset treated are moderate responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_SubsetResponders_mice_20pdanxamy.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Subset treated are moderate responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_SubsetResponders_humans_20pdanxamy.png", c, width=12, height=8)

```








```{r PCA 10% diff anx and amyg & most treated, eval=TRUE, message=FALSE}

dfm <- data.frame(matrix(nrow=28, ncol=7))
dfh <- data.frame(matrix(nrow=28, ncol=7))

names(dfm) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")
names(dfh) <- c("Subject", "Treatment", "Anxiety", "Memory", "Amygdala", "Striatum", "Thalamus")

dfm$Subject <- c(1:nrow(dfm))
dfm$Treatment <- c(rep("Tide",14), rep("Placebo", 14))
dfm$Responder <- c(rep("Responder",11), rep("Nonresponder", 17))
dfm$Anxiety <- c(rnorm(11, mean=31.1*1.4, sd=20.6),rnorm(17, mean=31.1, sd=20.6))
dfm$Memory <- rnorm(nrow(dfm), mean=51.5, sd=18.6)
dfm$Amygdala <- c(rnorm(11, mean=9.42*1.4, sd=.526),rnorm(17, mean=9.42, sd=.526))
dfm$Striatum <- rnorm(nrow(dfm), mean=20, sd=1.09)
dfm$Thalamus <- rnorm(nrow(dfm), mean=16.5, sd=0.917)

dfh$Subject <- c(1:nrow(dfh))
dfh$Treatment <- c(rep("Tide",14), rep("Placebo", 14))
dfh$Responder <- c(rep("Responder",11), rep("Nonresponder", 17))
dfh$Anxiety <- c(rnorm(11, mean=51.4*1.4, sd=17.7),rnorm(17, mean=51.4, sd=17.7))
dfh$Memory <- rnorm(nrow(dfh), mean=39.8, sd=9.97)
dfh$Amygdala <- c(rnorm(11, mean=1248*1.4, sd=220),rnorm(17, mean=1248, sd=220))
dfh$Striatum <- rnorm(nrow(dfh), mean=8944, sd=1636)
dfh$Thalamus <- rnorm(nrow(dfh), mean=6265, sd=999)




#mice

PCAb <- prcomp(dfm %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfm, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are strong responders on two measures",atop(italic("Principle Component Analysis- Mice"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_mice_10pdanxamy_smalln.png", c, width=12, height=8)




#humans

PCAb <- prcomp(dfh %>% select(-Subject,-Treatment, -Responder), scale=TRUE)

summary(PCAb)


plot(PCAb)

c <- autoplot(PCAb, data=dfh, colour="Treatment", size=3, loadings=TRUE, loadings.colour="black", loadings.label=TRUE, loadings.label.size=7, loadings.label.colour="black", shape="Responder") 
c <- c + theme_bw(35)
c <- c + scale_colour_hue(guide=FALSE)
c <- c + theme(legend.position="none")
c <- c + theme(legend.title= element_text(size=35))
#c <- c + theme(legend.text= element_text(size=20))
c <- c + ggtitle(expression(atop("Most treated are strong responders on two measures",atop(italic("Principle Component Analysis- Humans"),"")))) +  theme(plot.title = element_text(size = 35, face="bold", hjust=0.5))
c <- c + xlab("Component 1") + ylab("Component 2")
c

ggsave("CCP_Tideglusib_TestingML_PCA_NEW_MostResponders_humans_10pdanxamy_smalln.png", c, width=12, height=8)

```


